Northern Pikeminnow Predation on Juvenile Chinook Salmon in Deadwater Slough, Salmon River, Idaho and Potential Impacts to Local Populations

### 2022-01-14 analysis/paper/paper.Rmd
cleaned up the mess
Modified plot

Here's a mess!

@@

```{r abund-fig, fig.cap = "Estimates of abundance of Northern Pikeminnow using different mark-recapture estimators and for the fall sampling events. Single census estimators are shown as circles; multiple census estimators are shown as triangles. Note the y-axis is truncated at 100 and the upper confidence interval for the Schumacker-Eschmeyer estimator in 2020 extends beyond that."}
all_est %>%
  mutate(across(c(N, Lci, Uci),
                ~ . / 1000)) %>%
  mutate(census = case_when(grepl("Chapman", model) ~ "single",
                            grepl("Petersen", model) ~ "single",
                            grepl("Schnabel", model) ~ "multiple",
                            grepl("Schumacher-Eschmeyer", model) ~ "multiple")) %>%
  ggplot(aes(x = model,
             y = N,
             #color = model
             )) +
  geom_point(aes(size = 4,
                 shape = census)) +
  scale_shape_manual(values = c(17, 19)) +
  geom_errorbar(aes(ymin = Lci,
                    ymax = Uci),
                width = 0.1) +
  facet_wrap(~ event_name) +
  coord_cartesian(ylim = c(0, 100)) +
  labs(x = "Estimator",
       y = "Abundance (x 1,000)") +
  #theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45,
                                   hjust = 1,
                                   size = 11,
                                   color = "black"),
        axis.text.y = element_text(size = 11,
                                   color = "black"),
        strip.text.x = element_text(size = 11,
                                    color = "black")) +
  scale_color_brewer(palette = "Dark2")

>>>>

@@

```{r abund-fig, fig.cap = "Estimates of abundance of Northern Pikeminnow using different mark-recapture estimators and for the fall sampling events. Single census estimators are shown as circles; multiple census estimators are shown as triangles. Note the y-axis is truncated at 100 and the upper confidence interval for the Schumacker-Eschmeyer estimator in 2020 extends beyond that."}

pos = position_dodge(width=0.3)
all_est %>%

  mutate(across(c(N, Lci, Uci),
                ~ . / 1000)) %>%
  mutate(census = case_when(grepl("Chapman", model) ~ "single",
                            grepl("Petersen", model) ~ "single",
                            grepl("Schnabel", model) ~ "multiple",
                            grepl("Schumacher-Eschmeyer", model) ~ "multiple")) %>%

  ggplot(aes(x = model,
             y = N,
             #color = model
             )) +
  geom_errorbar(aes(ymin = Lci,ymax = Uci, group=event_name), position = pos, width=0) + 
  geom_point(aes(shape = event_name, color = census), position = pos, size = 4) +
    #facet_wrap(~ event_name) +
  coord_cartesian(ylim = c(0, 100)) +
  scale_shape_manual(values = c(21, 19), name="Event") +
  scale_color_manual(values = c("grey35", "darkred"), name="Census type") +
  labs(x = "Estimator",
       y = "Abundance (x 1,000)") +
  #scale_size(guide = "none")+
  theme(legend.position="top",legend.key = element_blank(),
        legend.background = element_blank(),
        legend.key.size = unit(0.50, "cm"),
        #axis.title.x = element_blank(),
        axis.text.x = element_text(angle = 45, hjust = 1, size = 11, color = "black"),
        axis.text.y = element_text(size = 11, color = "black"),
        strip.text.x = element_text(size = 11,color = "black"))
  #scale_color_brewer(palette = "Dark2")
